How to compute the fusion product of MV cycles in type $A$

### 2021-05-31 draft.tex
Comments on 6.3. New format for examples applied to Example 3.

%!TEX program = lualatex
% 
\documentclass{article} % [draft] TODO: use this at the end to check for overfills 
\usepackage{basic}
\usepackage{emoji}
% TODO: The matrix is lower triangular and the lower-triangular matrix is
% \setemojifont{Apple Color Emoji}
% Working title: 
\title{How to compute the fusion product of MV cycles in type $A$}
\author{Roger Bai, Anne Dranowski, Joel Kamnitzer} 
% \date{October 2020}
\date{\today}

@@

Throughout the paper, we fix $ m \in \NN$.  We let $G = \GL_m$ and let $T\subset G$ be the maximal torus of diagonal matrices. 
% are there other possibilities?? :S 
We identify $\ZZ^m$ with the coweight lattice of $G$ and say that a coweight 
% The coweight lattice of $ G $ is $ \ZZ^m = \Hom(\AA^\times,T)$.
% TODO: Thank you - resolved!
% \acom{This identification assumes we are taking $\CC$ points of $G$ right? i.e.\ it's really $P(T(\CC)) = \Hom(\AA^\times,T(\CC))$ that's $\cong \ZZ^m$ and for instance $P(T(\CC[x]/(x^2))$ will give sth else?} 
% \jcom{No, the coweight lattice is the set of homomorphisms of algebraic groups from $ \mathbb G_m$ to $ GL_m$.  It is independent of the ring/field of definition.}
% 
% The \textbf{dominant coweights} of $ G $ are the set of $ \lambda = (\lambda_1, \dots, \lambda_m) \in \ZZ^m $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$. 
% 
% A coweight $ \mu = (\mu_1, \dots, \mu_m) \in \ZZ^m$ is called \textbf{effective} if $ \mu_j \ge 0 $ for all $ j$.
% 
$\nu = (\nu_1,\dots,\nu_m)$ is \new{dominant} if $\nu_1\ge\cdots\ge\nu_m$ and \new{effective} if $\nu_j\ge 0$ for all $j$.
% We also need the notion of effective dominant coweight, 
% \acom{can we conflate or should we be precise and say coweight?} \jcom{Corrected, let's stick to coweights.}
%which means those $ \lambda $ as above with $ \lambda_m \ge 0$.  
% \acom{1. No boldface on this new term. Proceed with selective boldfacing? 2. Since we sometimes need $\Peff$ which contains $P_{++} = \Peff\cap\Pdom$, how about just using the notation $\Peff,\Pdom$ instead of $P_+, P_{++}$ for a change?}
% \jcom{I added the definition of effective coweight.  I actually don't think that we need any special notation $ P, P_+, P_{dom}$ etc !  Later we can just write ``$ \lambda \in \ZZ^m$ a dominant or effective coweight'' etc}
% TODO: it's settled then, no special notation fro coweights!
% 
If $\nu\in\ZZ^m$ is both effective and dominant then it is a partition of size $|\nu| = \nu_1 + \cdots + \nu_m\in\NN$.
%We write $P_+$ for the set of dominant coweights, and $P_{++}$ for the set of effective dominant coweights. 
% 
% nicematrix test
% $\begin{bNiceArray}{ccc|c}[margin]
%     \Block{3-3}<\Large>{A} & & & 0 \\
%     & \hspace*{1cm} & & \Vdots \\
%     & & & 0 \\
%     \hline
%     0 & \Cdots& 0 & 0
%     \end{bNiceArray}$
% 
% $\begin{pNiceMatrix}
%     \frac12 & -\frac12 \\
%     \frac13 & \frac14 \\
%     \end{pNiceMatrix}$
% 
% Set $\AA = \AA^1_x$ (the subscript denoting the chosen local coordinate) and fix $s\in \AA - \{0\}$. 
% 
% Given a coweight $\mu \in \ZZ^m$ and a point $ s\in \CC$, we define $ (t-s)^\mu$ to be the diagonal matrix 
Given $s\in\CC$ we define $(t-s)^\nu$ to be the diagonal matrix 
% with entries $ (t-s)^{\mu_1}, \dots, (t-s)^{\mu_m}$
% \[
%     \begin{pNiceMatrix}[nullify-dots,xdots/line-style=loosely dotted]
%         (t-s)^{\mu_1} & 0             & \Cdots & 0 \\
%         0             & (t-s)^{\mu_2} & \Ddots & \Vdots \\
%         % 0 & b & a & \Ddots & & \\
%         \Vdots              & \Ddots        & \Ddots & 0 \\
%         % \Vdots & & & & \\
%         0             & \Cdots        &   0    & (t-s)^{\mu_m}
%     \end{pNiceMatrix}
% \]
\[
\begin{bmatrix}
    (t-s)^{\nu_1} \\
    & (t-s)^{\nu_2} \\ 
    & & \ddots \\
    & & & (t-s)^{\nu_m}
\end{bmatrix} 
\]
which we can view in 
% $\GL_m(K) $ 
$G(K)$ for any ring $ K $ containing $(t-s)^{-1}$ and $\CC[t]$. For example, $(t-s)^\nu\in G(K)$ for $ K = \Ks$ or $\CC(t)$. % A: Think R sb K; changed it

@@

\subsection{Lattices}
\label{ss:lat}
We will use the lattice model for the affine Grassmannian, so it is useful to recall the following definition. Let $ R \subset K$ be two $\CC$-algebras (usually, but not always, $K$ will be a field). 
% \acom{When is $K$ not a field?}). Let $ m \in \mathbb N$ \acom{we have already fixed $m$?} and; e.g. K = C[t,t^{-1}] is not a field!!! 
Consider $ K^m $ as a $K$-module. 
% \acom{left or right, doesn't matter? I think we are in a situation where they are the same, i.e.\ our rings are commutative.} 
By restriction $ K^m$ can be viewed as an $R$-module.  An \textbf{$R$-lattice} in $K^m$ 
% \acom{what is $M$? should be $K^m$?}; bc Joel was thinking about arbitrary free modules 
is an $R$-submodule $ L \subset K^m$ 
% such that $ L $ 
which is a free $R$-module of rank $ m $ and satisfies $ L \otimes_R K = K^m $. Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$. 
% 
\begin{comment}
\jcom{Maybe need that both $K$ and $R$ are integral domains and have the same field of fractions?} 
\acom{Roger has proved that what is written is ok.}
\rcom{Here's my argument: If $L \subset K^m$ is a free rank $m$ $R$-module and $L \otimes K = K^m$, then it's clear we that $L$ is generated by $m$ generators $v_1,\dots,v_m$ over $R$. Since $L\otimes K = K^m$, these also generate $K^m$ over $K$. Then we have a surjective map $K^m \twoheadrightarrow K^m$ given by sending a basis of $K^m$ to the generators $v_1,\dots,v_m$. Since any surjective endomorphism of finite $K$-modules is injective, the $v_1,\dots,v_m$ form a basis. I think the only thing that is needed is that the rings are commutative.}
\jcom{Great.}
\end{comment}

@@

We will be particularly interested in $\CC[t]$-lattices in $ \CC(t)^m$. 
% TODO: 
% \acom{Wait, I thought $\CC(t)$ is used in the Ran space version of the BD Gr.}
Given such a lattice $ L $ and a point $ a \in \CC$, the \textbf{specialization} of $ L $ at $ a $ is the lattice in $\cK_a^m$ defined as $ L(a) := L \otimes_{\CC[t]} \cO_a $. 
If $L(a) = \cO_a^m$ then $L$ is said to be \textbf{trivial at $a$}. 
% We say that $ L $ is trivial at $ a $ if $ L(a) = \cO_a^m$. 
% \acom{Do we want to employ the notation $\cO_a$ and $\cK_a$ here?}
For example, the lattice $(t-s)^{-1}\CC[t] \subset \CC(t)$ is trivial at any $a\ne s$, since $ t-s $ is invertible in $ \cO_a$. 
% \acom{it is a little bit uneven to have notation for $\cO^m$ but not for $\cO_a^m$?}

@@

     The \textbf{ordinary affine Grassmannian} $\Gr = G(\cK)/G(\cO)$.

@@

    the \textbf{ordinary affine Grassmannian} $\Gr_s = G(\cK_s)/G(\cO_s)$ \textbf{at} $ s $. 

@@

The \textbf{thick affine Grassmannian} $\Grth = G(\Kinf)/G(\CC[t])$.

@@

The two point \textbf{Beilinson--Drinfeld Grassmannian} $$\pi : \Grbd\to \AA$$ with one point fixed at 0, and the second point $s\in\AA$ varying.

@@

The \textbf{positive part} of $\Gr $, resp.\ $\Grth$, is defined by 

@@

The fibre $ X_1 \ast_0 X_2$ of $ X_1 \ast_{\AA} X_2 $ over $0$ is a subscheme of $ \Gr_{0,0} $, but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.  We call this subscheme the \textbf{fusion} of $ X_1 $ and $ X_2$.

% \jcom{I rewrote this to introduce the $ X_1 \ast_s X_2 $ notation that we need for later.  In doing so, $ X_1 \circ X_2 $ became obsolete, since we now have $ X_1 \ast_0 X_2$, but if you like we could just define $X_1 \circ X_2 = X_1 \ast_0 X_2 $.}
% 
% Next, we consider the projection $ \pi: \Grbd \rightarrow \AA $, and define 
% $ X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) \subset \Gr_{0,0} $, 
% \begin{equation*}
    % \label{deservesdisplay}
%    X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) 
% \end{equation*}
% which we call the \textbf{fusion} of $ X_1 $ and $X_2$. It is contained in $\Gr_{0,0}$ but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.  
% 
% By construction, 
% \acom{technically, there were two given above, so *these* constructions?} 
% $X_1 \ast_{\AA} X_2 $ is a flat family over $\AA$ whose fibre away from $0$ is $X_1 \times X_2$ and whose fibre over $ 0$ is $ X_1 \circ X_2$.

@@

    The \textbf{spherical Schubert cell} $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 

@@

    a \textbf{spherical Schubert variety}.  

@@

    The \textbf{BD family of two spherical Schubert varieties} $\overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} $.

@@

\begin{definition}
\label{def:klslice}
    The \textbf{Kazhdan--Lusztig slice} $\cW_\mu = G_1(\Oinf) t^\mu \subset \Grth $.  
\end{definition}
%

@@

% \acom{First lattice description that doesn't come for free?}
% 
% \acom{que est-ce?} \jcom{It's not very relevant for this paper.  Here is an explanation: every vector bundle on $\PP$ (or maybe any curve) has a special filtration called the HN--filtration; it is a partial flag of subbundles of type determined by $ \mu$.  We require that $ \varphi$ takes this filtration to the standard partial flag at the fibre over $ \infty$.  Maybe ``preserves'' is not the best word above.}
% A: Ok thanks!
% 
\begin{definition} 
\label{def:inftyorbits}
    The \textbf{semi-infinite orbit} $ S^\mu = N_-(\cK)t^\mu \subset \Gr $ and the \textbf{family of two semi-infinite orbits} 
 $S^{\mu', \mu''}_{0,\AA} \subset \Grbd$
 which we define to have fibres $ S^{\mu'} \ast_s S^{\mu''}_s $ for $ s \ne 0$ and fibre $ S^{\mu}$ over $ s = 0 $.
\end{definition}
Note that since $ S^{\mu}$ is not closed, it is not true that $S^{\mu', \mu''}_{0,\AA} = S^{\mu'} \ast_\AA S^{\mu''}$.
% 
%\acom{Commented out fusion part for now. Unsure about defining it as the family whose 0 fibre is $S^{\mu' + \mu''}$ and whose generic fibre is $S^{\mu'}\times S^{\mu''}$ up to $\tau$. Baumann--Riche consider the attracting set of $C_\mu = \sqcup_{\mu' + \mu'' = \mu } m(\tilde C_{\mu',\mu''})$ where $\tilde C_{\mu',\mu''}$ is a connected component of fixed points in $\Grbd\tilde\times\Grbd$. Maybe we can consider the attracting set of just one of these?}
% 
If $ s \ne 0 $, then the fibre $S^{\mu', \mu''}_{0,s} $ is given by
$$
% S^{\mu', \mu''}_{0,s} = 
    N_-(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu'} (t-s)^{\mu''} G(\CC[t])\subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
$$
See section 5.2 of \cite{baumann2020bases} for further details.

@@

Recall that $\mu=(\mu_1,\dots,\mu_m)$ is a partition of $N$. The \textbf{Mirkovi\'c--Vybornov slice} $\TT_\mu$ is the affine space of $N\times N$ matrices of the form

@@

In $\TT_\mu$ we will be interested in a certain family of block upper-triangular matrices.
\begin{definition} The ``\textbf{upper-triangular}'' \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $, defined by
$$
\UU^{\mu', \mu''}_{0,\AA} := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu'_{i}} (t-s)^{\mu''_{i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}\,. 
$$
\end{definition}
So a matrix in $\UU^{\mu', \mu''}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu'_{i}} (t-s)^{\mu''_{i}}$ ($i=1,\dots,m$).

@@

Restricting to the zero fibre and applying $\theta_0$ we recover \cite[Corollary~5.2.2]{dthesis}. 
%itself a corollary of \cite[Theorem~4.4.1(c)]{mirkovic2019comparison}, the ordinary affine Grassmannian version of \Cref{th:OGrl}. 
% 
% \acom{The ordinary Gr should be called static. Really onomotopoeic. In opposition with moving. }
% 
\begin{corollary}
    \label{cor:mvy}
The map $ A \mapsto g(A)\OO^m$ gives an isomorphism    $\overline{\OO}^\lambda \cap \TT_\mu\cap\n \cong\overline\Gr^\lambda\cap S^\mu_-$.
\end{corollary}
%The closures of the irreducible components of the righthand side are \textbf{MV cycles of type $\lambda$ and weight $\mu$}. By \cite{baumann2019mirkovic} the set of MV cycles of all possible types and weights can be stitched together to form a \textbf{perfect basis} of $\CC[N]$.

@@

\section{\sout{Falling Action}} % Resolution
\subsection{MV cycles}
% 
% We need to decide on the order in section 7. How about:
% 
% 1. MV cycles and tableaux (7.1)
% 2. GOVs and relation to MV cycles, including fusion (7.2)
% 3. Stable MV cycles and multiplication  in C[N]
% 
\begin{definition}
An irreducible component of $\overline{\Gr}^\lambda \cap S^\mu$ is called an \textbf{Mirkovic--Vilonen cycle} in $\overline{\Gr}^\lambda$ of coweight $\mu$.
\end{definition}

\jcom{In this section, I think that $ \mu$ is not necessarily dominant.  So I think that we should we recall our previous notation, but say that $ \mu $ might not be dominant here.}
\acom{Ok.}

By \cite{mirkovic2007geometric}, all these irreducible components have dimension $ \rho(\lambda - \mu)$, where $ \rho = (m, m-1, \dots, 1)$.

@@

From  the proof of \cite[Proposition 9.6]{kamnitzer2010mirkovic}, we see that $ \mathring Z(\tau)_1$ is equal to $ t^\mu A(n_\bullet(\tau))$, where $ A(n_\bullet)$ is defined in section 4.3 of \cite{kamnitzer2010mirkovic}. In particular it is irreducible. Thus, its closure is the MV cycle whose Lusztig datum is $ n_\bullet(\tau) $. (In \cite{kamnitzer2010mirkovic}, the third author worked with $  G(\cO) \backslash G(\cK)$, which we identify with $ \Gr $ using the map $ G(\cO) g \mapsto g^{-1} G(\cO)$.) 
% \acom{Maybe we should avoid using square brackets as we haven't used them yet?}

Now, by the results of \cite{kamnitzerfibreshives} (see especially the proof of Theorem 1.4), we note that $\mathring Z(\tau)_1\cap \Gr^\lambda$ is dense in $ \mathring Z(\tau)_1$.

@@

Let $\tau\in YT(\lambda)_\mu$ with $\mu$ dominant. 
We define
\[
\mathring X(\tau) = 
% \overline{
    \{
        A \in  \TT_\mu\cap\n : A\big|_{\CC^{|\mu(i)|}} \in \OO^{\lambda(i)} \text{ for each } i = 1,\dots,m
    \}\,.
\]
\jcom{Maybe for consistency, we should write $ \n \cap \TT_\mu$ (opposite order).}

\begin{lemma}
    \label{lem:XtZt}
    Under the Mirkovi\'c--Vybornov isomorphism $\mathring X(\tau)$ is mapped isomorphically onto $\mathring Z(\tau)$. 
\end{lemma}
\jcom{We should add a proof here.  It will be very similar to Prop 5 below.}

>>>>

%!TEX program = lualatex
% 
\documentclass{article} % [draft] TODO: use this at the end to check for overfills 
\usepackage{basic}
\usepackage{emoji}
\usepackage{float}
% TODO: The matrix is lower triangular and the lower-triangular matrix is
% \setemojifont{Apple Color Emoji}
% Working title: 
\title{How to compute the fusion product of MV cycles in type $A$}
\author{Roger Bai, Anne Dranowski, Joel Kamnitzer} 
% \date{October 2020}
\date{\today}

@@

Throughout the paper, we fix $ m \in \NN$.  We let $G = \GL_m$ and let $T\subset G$ be the maximal torus of diagonal matrices. 
% are there other possibilities?? :S 
We identify $\ZZ^m$ with the coweight lattice of $G$ and say that a coweight 
% The coweight lattice of $ G $ is $ \ZZ^m = \Hom(\AA^\times,T)$.
% TODO: Thank you - resolved!
% \acom{This identification assumes we are taking $\CC$ points of $G$ right? i.e.\ it's really $P(T(\CC)) = \Hom(\AA^\times,T(\CC))$ that's $\cong \ZZ^m$ and for instance $P(T(\CC[x]/(x^2))$ will give sth else?} 
% \jcom{No, the coweight lattice is the set of homomorphisms of algebraic groups from $ \mathbb G_m$ to $ GL_m$.  It is independent of the ring/field of definition.}
% 
% The \new{dominant coweights} of $ G $ are the set of $ \lambda = (\lambda_1, \dots, \lambda_m) \in \ZZ^m $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$. 
% 
% A coweight $ \mu = (\mu_1, \dots, \mu_m) \in \ZZ^m$ is called \new{effective} if $ \mu_j \ge 0 $ for all $ j$.
% 
$\nu = (\nu_1,\dots,\nu_m)$ is \new{dominant} if $\nu_1\ge\cdots\ge\nu_m$ and \new{effective} if $\nu_j\ge 0$ for all $j$.
% We also need the notion of effective dominant coweight, 
% \acom{can we conflate or should we be precise and say coweight?} \jcom{Corrected, let's stick to coweights.}
%which means those $ \lambda $ as above with $ \lambda_m \ge 0$.  
% \acom{1. No boldface on this new term. Proceed with selective boldfacing? 2. Since we sometimes need $\Peff$ which contains $P_{++} = \Peff\cap\Pdom$, how about just using the notation $\Peff,\Pdom$ instead of $P_+, P_{++}$ for a change?}
% \jcom{I added the definition of effective coweight.  I actually don't think that we need any special notation $ P, P_+, P_{dom}$ etc !  Later we can just write ``$ \lambda \in \ZZ^m$ a dominant or effective coweight'' etc}
% TODO: it's settled then, no special notation fro coweights!
% 
If $\nu\in\ZZ^m$ is both effective and dominant then it is a partition of size $|\nu| = \nu_1 + \cdots + \nu_m\in\NN$.
%We write $P_+$ for the set of dominant coweights, and $P_{++}$ for the set of effective dominant coweights. 
% 
% nicematrix test
% $\begin{bNiceArray}{ccc|c}[margin]
%     \Block{3-3}<\Large>{A} & & & 0 \\
%     & \hspace*{1cm} & & \Vdots \\
%     & & & 0 \\
%     \hline
%     0 & \Cdots& 0 & 0
%     \end{bNiceArray}$
% 
% $\begin{pNiceMatrix}
%     \frac12 & -\frac12 \\
%     \frac13 & \frac14 \\
%     \end{pNiceMatrix}$
% 
% Set $\AA = \AA^1_x$ (the subscript denoting the chosen local coordinate) and fix $s\in \AA - \{0\}$. 
% 
% Given a coweight $\mu \in \ZZ^m$ and a point $ s\in \CC$, we define $ (t-s)^\mu$ to be the diagonal matrix 
Given $s\in\CC$ we define $(t-s)^\nu$ to be the diagonal matrix 
% with entries $ (t-s)^{\mu_1}, \dots, (t-s)^{\mu_m}$
% \[
%     \begin{pNiceMatrix}[nullify-dots,xdots/line-style=loosely dotted]
%         (t-s)^{\mu_1} & 0             & \Cdots & 0 \\
%         0             & (t-s)^{\mu_2} & \Ddots & \Vdots \\
%         % 0 & b & a & \Ddots & & \\
%         \Vdots              & \Ddots        & \Ddots & 0 \\
%         % \Vdots & & & & \\
%         0             & \Cdots        &   0    & (t-s)^{\mu_m}
%     \end{pNiceMatrix}
% \]
\[
\begin{bmatrix}
    (t-s)^{\nu_1} \\
    & (t-s)^{\nu_2} \\ 
    & & \ddots \\
    & & & (t-s)^{\nu_m}
\end{bmatrix} 
\]
which we can view in 
% $\GL_m(K) $ 
$G(K)$ for any ring $ K $ containing $(t-s)^{-1}$ and $\CC[t]$. For example, $(t-s)^\nu\in G(K)$ for $ K = \Ks$ or $\CC(t)$. % A: Think R sb K; changed it

@@

\subsection{Lattices}
\label{ss:lat}
We will use the lattice model for the affine Grassmannian, so it is useful to recall the following definition. Let $ R \subset K$ be two $\CC$-algebras (usually, but not always, $K$ will be a field). 
% \acom{When is $K$ not a field?}). Let $ m \in \mathbb N$ \acom{we have already fixed $m$?} and; e.g. K = C[t,t^{-1}] is not a field!!! 
Consider $ K^m $ as a $K$-module. 
% \acom{left or right, doesn't matter? I think we are in a situation where they are the same, i.e.\ our rings are commutative.} 
By restriction $ K^m$ can be viewed as an $R$-module.  An \new{$R$-lattice} in $K^m$ 
% \acom{what is $M$? should be $K^m$?}; bc Joel was thinking about arbitrary free modules 
is an $R$-submodule $ L \subset K^m$ 
% such that $ L $ 
which is a free $R$-module of rank $ m $ and satisfies $ L \otimes_R K = K^m $. Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$. 
% 
\begin{comment}
\jcom{Maybe need that both $K$ and $R$ are integral domains and have the same field of fractions?} 
\acom{Roger has proved that what is written is ok.}
\rcom{Here's my argument: If $L \subset K^m$ is a free rank $m$ $R$-module and $L \otimes K = K^m$, then it's clear we that $L$ is generated by $m$ generators $v_1,\dots,v_m$ over $R$. Since $L\otimes K = K^m$, these also generate $K^m$ over $K$. Then we have a surjective map $K^m \twoheadrightarrow K^m$ given by sending a basis of $K^m$ to the generators $v_1,\dots,v_m$. Since any surjective endomorphism of finite $K$-modules is injective, the $v_1,\dots,v_m$ form a basis. I think the only thing that is needed is that the rings are commutative.}
\jcom{Great.}
\end{comment}

@@

We will be particularly interested in $\CC[t]$-lattices in $ \CC(t)^m$. 
% TODO: 
% \acom{Wait, I thought $\CC(t)$ is used in the Ran space version of the BD Gr.}
Given such a lattice $ L $ and a point $ a \in \CC$, the \new{specialization} of $ L $ at $ a $ is the lattice in $\cK_a^m$ defined as $ L(a) := L \otimes_{\CC[t]} \cO_a $. 
If $L(a) = \cO_a^m$ then $L$ is said to be \new{trivial at $a$}. 
% We say that $ L $ is trivial at $ a $ if $ L(a) = \cO_a^m$. 
% \acom{Do we want to employ the notation $\cO_a$ and $\cK_a$ here?}
For example, the lattice $(t-s)^{-1}\CC[t] \subset \CC(t)$ is trivial at any $a\ne s$, since $ t-s $ is invertible in $ \cO_a$. 
% \acom{it is a little bit uneven to have notation for $\cO^m$ but not for $\cO_a^m$?}

@@

     The \new{ordinary affine Grassmannian} $\Gr = G(\cK)/G(\cO)$.

@@

    the \new{ordinary affine Grassmannian} $\Gr_s = G(\cK_s)/G(\cO_s)$ \new{at} $ s $. 

@@

The \new{thick affine Grassmannian} $\Grth = G(\Kinf)/G(\CC[t])$.

@@

The two point \new{Beilinson--Drinfeld Grassmannian} $$\pi : \Grbd\to \AA$$ with one point fixed at 0, and the second point $s\in\AA$ varying.

@@

The \new{positive part} of $\Gr $, resp.\ $\Grth$, is defined by 

@@

The fibre $ X_1 \ast_0 X_2$ of $ X_1 \ast_{\AA} X_2 $ over $0$ is a subscheme of $ \Gr_{0,0} $, but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.  We call this subscheme the \new{fusion} of $ X_1 $ and $ X_2$.

% \jcom{I rewrote this to introduce the $ X_1 \ast_s X_2 $ notation that we need for later.  In doing so, $ X_1 \circ X_2 $ became obsolete, since we now have $ X_1 \ast_0 X_2$, but if you like we could just define $X_1 \circ X_2 = X_1 \ast_0 X_2 $.}
% 
% Next, we consider the projection $ \pi: \Grbd \rightarrow \AA $, and define 
% $ X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) \subset \Gr_{0,0} $, 
% \begin{equation*}
    % \label{deservesdisplay}
%    X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) 
% \end{equation*}
% which we call the \new{fusion} of $ X_1 $ and $X_2$. It is contained in $\Gr_{0,0}$ but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.  
% 
% By construction, 
% \acom{technically, there were two given above, so *these* constructions?} 
% $X_1 \ast_{\AA} X_2 $ is a flat family over $\AA$ whose fibre away from $0$ is $X_1 \times X_2$ and whose fibre over $ 0$ is $ X_1 \circ X_2$.

@@

    The \new{spherical Schubert cell} $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 

@@

    a \new{spherical Schubert variety}.  

@@

    The \new{BD family of two spherical Schubert varieties} $\overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} $.

@@

\begin{definition}
\label{def:klslice}
    The \new{Kazhdan--Lusztig slice} $\cW_\mu = G_1(\Oinf) t^\mu \subset \Grth $.  
\end{definition}
%

@@

% \acom{First lattice description that doesn't come for free?}
% 
% \acom{que est-ce?} \jcom{It's not very relevant for this paper.  Here is an explanation: every vector bundle on $\PP$ (or maybe any curve) has a special filtration called the HN--filtration; it is a partial flag of subbundles of type determined by $ \mu$.  We require that $ \varphi$ takes this filtration to the standard partial flag at the fibre over $ \infty$.  Maybe ``preserves'' is not the best word above.}
% A: Ok thanks!
% 
\begin{definition} 
\label{def:inftyorbits}
    The \new{semi-infinite orbit} $ S^\mu = N_-(\cK)t^\mu \subset \Gr $ and the \new{family of two semi-infinite orbits} 
 $S^{\mu', \mu''}_{0,\AA} \subset \Grbd$
 which we define to have fibres $ S^{\mu'} \ast_s S^{\mu''}_s $ for $ s \ne 0$ and fibre $ S^{\mu}$ over $ s = 0 $.
\end{definition}
Note that since $ S^{\mu}$ is not closed, it is not true that $S^{\mu', \mu''}_{0,\AA} = S^{\mu'} \ast_\AA S^{\mu''}$.
% 
%\acom{Commented out fusion part for now. Unsure about defining it as the family whose 0 fibre is $S^{\mu' + \mu''}$ and whose generic fibre is $S^{\mu'}\times S^{\mu''}$ up to $\tau$. Baumann--Riche consider the attracting set of $C_\mu = \sqcup_{\mu' + \mu'' = \mu } m(\tilde C_{\mu',\mu''})$ where $\tilde C_{\mu',\mu''}$ is a connected component of fixed points in $\Grbd\tilde\times\Grbd$. Maybe we can consider the attracting set of just one of these?}
% 
If $ s \ne 0 $, then the fibre $S^{\mu', \mu''}_{0,s} $ is given by
$$
% S^{\mu', \mu''}_{0,s} = 
    N_-(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu'} (t-s)^{\mu''} G(\CC[t])\subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
$$
See section 5.2 of \cite{baumann2020bases} for further details.

@@

Recall that $\mu=(\mu_1,\dots,\mu_m)$ is a partition of $N$. The \new{Mirkovi\'c--Vybornov slice} $\TT_\mu$ is the affine space of $N\times N$ matrices of the form

@@

In $\TT_\mu$ we will be interested in a certain family of block upper-triangular matrices.
\begin{definition} The ``\new{upper-triangular}'' \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $, defined by
$$
\UU^{\mu', \mu''}_{0,\AA} := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu'_{i}} (t-s)^{\mu''_{i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}\,. 
$$
\end{definition}
So a matrix in $\UU^{\mu', \mu''}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu'_{i}} (t-s)^{\mu''_{i}}$ ($i=1,\dots,m$).

@@

Restricting to the zero fibre and applying $\theta_0$ we recover \cite[Corollary~5.2.2]{dthesis}. 
%itself a corollary of \cite[Theorem~4.4.1(c)]{mirkovic2019comparison}, the ordinary affine Grassmannian version of \Cref{th:OGrl}. 
% 
% \acom{The ordinary Gr should be called static. Really onomotopoeic. In opposition with moving. }
% 
\begin{corollary}
    \label{cor:mvy}
The map $ A \mapsto g(A)\OO^m$ gives an isomorphism    $\overline{\OO}^\lambda \cap \TT_\mu\cap\n \cong\overline\Gr^\lambda\cap S^\mu_-$.
\end{corollary}
%The closures of the irreducible components of the righthand side are \new{MV cycles of type $\lambda$ and weight $\mu$}. By \cite{baumann2019mirkovic} the set of MV cycles of all possible types and weights can be stitched together to form a \new{perfect basis} of $\CC[N]$.

@@

\section{\sout{Falling Action}} % Resolution
\subsection{MV cycles}
Let $\lambda\ge\mu$ be dominant effective and effective coweights of $\GL_m$ respectively. 
% 
% We need to decide on the order in section 7. How about:
% 
% 1. MV cycles and tableaux (7.1)
% 2. GOVs and relation to MV cycles, including fusion (7.2)
% 3. Stable MV cycles and multiplication  in C[N]
% 
\begin{definition}
An irreducible component of $\overline{\Gr}^\lambda \cap S^\mu$ is called an \new{Mirkovic--Vilonen cycle} in $\overline{\Gr}^\lambda$ of coweight $\mu$.
\end{definition}

% \jcom{In this section, I think that $ \mu$ is not necessarily dominant.  So I think that we should we recall our previous notation, but say that $ \mu $ might not be dominant here.}
% \acom{Ok.}

By \cite[Theorem~3.2(b)]{mirkovic2007geometric}, each MV cycle has in $\overline\Gr^\lambda$ of coweight $\mu$ has dimension $ \rho(\lambda - \mu)$ where $\rho$ is the half sum of positive roots. Normalizing $ \rho = (m, m-1, \dots, 1)$ and identifying $P \cong P^\vee$ the pairing $P\times P^\vee\to\ZZ $ is given by the ordinary dot product.

@@

From  the proof of \cite[Proposition 9.6]{kamnitzer2010mirkovic}, we see that $ \mathring Z(\tau)_1$ is equal to $ t^\mu A(n_\bullet(\tau))$, where $ A(n_\bullet)$ is defined in Sect.\ 4.3 of \cite{kamnitzer2010mirkovic}. In particular, it is irreducible. Thus, its closure is the MV cycle whose Lusztig datum is $ n_\bullet(\tau) $. (The reader is warned that in \cite{kamnitzer2010mirkovic} the third author worked with $  G(\cO) \backslash G(\cK)$, which we identify with $ \Gr $ using the map $ G(\cO) g \mapsto g^{-1} G(\cO)$.) 
% \acom{Maybe we should avoid using square brackets as we haven't used them yet?}
% 
Now, by results of \cite{kamnitzer2008hives}, (see especially the proof of Theorem 1.4,) we note that $\mathring Z(\tau)_1\cap \Gr^\lambda$ is dense in $ \mathring Z(\tau)_1$. 
% Explanation: 
% MV polytopes giving tensor product multiplicity of V(\nu) in
% V(\lambda) \otimes V(\mu)
% with
% Hives with bdy \lambda, \mu, \nu.
% 
% If we take \mu and \nu to be sufficiently large compared to \lambda,
% then this becomes a bijection
% MV polytopes for the weight multiplicity V(\lambda)_{\nu - \mu}
% with
% Young tableaux YT(\lambda)_{\nu - \mu}
% 
% Even better, in that paper, I worked geometrically, and I gave a
% bijection from components of the fibre of the convolution morphism to
% hives.  Again, taking \mu, \nu large compared to \lambda, this fibre
% of the convolution morphism becomes Gr^\lambda \cap S^{\nu - \mu}.  So
% that paper actually does give a bijection from components of
% Gr^\lambda \cap S^{\nu - \mu} to tableaux.

@@

Let $\tau\in YT(\lambda)_\mu$ with $\mu$ dominant. 
We define
\[
\mathring X(\tau) = 
% \overline{
    \{
        A \in  \TT_\mu\cap\n : A\big|_{\CC^{|\mu(i)|}} \in \OO^{\lambda(i)} \text{ for each } i = 1,\dots,m
    \}\,.
\]
